---
title: "A_map_drawing_tool_with_DrawRmap"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A_map_drawing_tool_with_DrawRmap}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

'DrawRmap' is a mapping function that allows the user to obtain the map by specifying the location, map type, and zoom level.

# Load packages

```{r setup}
install.packages(c("ggmap", "httr", "jsonlite"))
library(CntoAPI)
```

# Example: Mapping Asia

```{r drawRmap}
drawRmap("Asia", maptype = "stamen_toner", zoom = 10)
```

# Function parameter

The parameters of the drawRmap function are as follows:

location: A string that specifies where to draw the map.

maptype: A string that specifies the type of the map. Valid options include:
stamen_toner
stamen_toner_lite
stamen_watercolor
stamen_terrain
stamen_terrain_background
stamen_terrain_labels
stamen_terrain_lines
outdoors
alidade_smooth
alidade_smooth_dark

zoom: Numeric, zoom level, ranging from 1 to 20.

# Error handling

When calling the drawRmap function, you may encounter some error situations:
An error is thrown if an invalid map type is provided.
If the zoom level provided is not in the range of 1 to 20, an error is thrown.
If the latitude and longitude of the specified location cannot be obtained, an error is thrown.

# Conclusion

The drawRmap function makes it easy to map the desired location. Adjust the parameters as needed to get different types of maps.